Timeliness of security updates for Android and Chrome

### 2014-02-07 securityupdates.tex
Replace abstract and start talking about Chrome

\begin{abstract}
Android is the most popular smartphone platform and seeks to provide better security than popular desktop operating systems through increased compartmentalisation and a permission system for apps.
This security relies on there not being root privilege exploits which allow apps to bypass all protections.
Many such exploits have been found and fixed.
Our hypothesis is that these fixes do not promptly reach the users devices and so much of the time users are running versions of Android known to be vulnerable.
We used the DeviceAnalyzer data\cite{TODO} and found that on average over XX\% of devices were exposed to known vulnerabilities. %TODO (drt24) proportion of devices exposed on average.
There was also a period of several months when no devices ran secure versions of Android.
\end{abstract}

\section{Introduction}
Android has XX\% of the smartphone market~\cite{TODO} and while the core development is controlled by Google there are at least XX~\cite{TODO} manufacturers which make devices which run Android.
Many of these manufacturers customise the version of Android they ship and sometimes network operators (of which there are at least XX~\cite{TODO}) make further modifications.
Hence when Google produces an update to Android, the update may have to pass through the manufacturer and operator before reaching the user.
The manufacturer and user have no financial incentive to perform this work.
There is ongoing legal action to force some of them to do so~\cite{TODO}.

@@

Figure \ref{fig:proportioninsecure} shows the proportion of Android devices in the DeviceAnalyzer data which were running versions of Android known to root exploits at the time.
In \S\ref{sec:background} we will explain where these data comes from and then in \S\ref{sec:results} we will show these data in more detail.

>>>>

\begin{abstract}
We examine two platforms which attempt to enforce fine grained permissions for arbitrary code which runs on them: Android and Chrome.
We compare the vulnerabilities find in them which break the sandbox with the distributions of versions running in the wild.
We find that on average \percArdInsec\ of Android and \percCrmInsec\ of Chrome instances are vulnerable to known security vulnerabilities which break their sandbox, there was a period of several months when all Android devices were vulnerable.
We examine some of the differences in incentives between the two platforms and how this has affected update timeliness.
For Android we compare different manufacturers to find those best at shipping updates promptly.
\end{abstract}

\section{Introduction}
Android has \percArdMarketShare\ of the smartphone market~\cite{TODO} and while the core development is controlled by Google there are at least \daNumManufacturers\ manufacturers which make devices which run Android.
Many of these manufacturers customise the version of Android they ship and sometimes network operators (of which there are at least \daNumNetworkOperators) make further modifications.
Hence when Google produces an update to Android, the update may have to pass through the manufacturer and operator before reaching the user.
The manufacturer and user have no financial incentive to perform this work.
There is ongoing legal action to force some of them to do so~\cite{TODO}.

@@

Figure \ref{fig:proportioninsecure} shows the proportion of Android devices in the DeviceAnalyzer data which were running versions of Android known to root exploits at the time.

Google's Chrome Web browser has \percCrmMarketShare\ of the web browser market~\cite{TODO}, its core development is controlled by Google and Google is the only major distributor of it (the open source Chromium project from which it is derived does not have many direct users).%TODO unsubstantiated assertion

Chrome uses various different sandboxing methods on different platforms such as Capsicum on BSD~\cite{TODO}

In \S\ref{sec:background} we will explain where these data comes from and then in \S\ref{sec:results} we will show these data in more detail.
